---
title: Position Sizing
author:
  - name: Nanthawat Anancharoenpakorn
abstract:
  - "Learn how to bet properly" 
  - "**Motivation:** In investment, one of the decision we have to make is how much to bet"

#boxedlist: # Not fully compatible with all document formats
#  - First point
#  - Second point
competing_interests: |
  There are no competing interest.
author_contributions: |
  AA did all the work. The others are just freeloaders.
acknowledgements: |
  This is an acknowledgement.

  It consists of two paragraphs.

bibliography: mybibfile.bib # Includes refs in OUP example template
## When using `citation_package = "default"`, a CSL file can be used
#csl: https://www.zotero.org/styles/oxford-university-press-note
output:
  rticles::oup_article:
    oup_version: 1 # 1 = 2020 CTAN OUP CLS package; 0 = 2009 OUP CLS package
    journal: "Journal Name"
    document_style: "contemporary" # Can be contemporary, modern, traditional
    papersize: "large" # Can be large, medium, small
    #citation_package: "default" # Uncomment when using a CSL; default "natbib"
    namedate: TRUE # Set FALSE to use numeric refs; Default FALSE
    #number_sections: FALSE # Uncomment to not number sections; default TRUE
    #number_lines: TRUE # Use `lineno` package - Default FALSE
    #number_lines_options: ["mathlines","switch"]  # Options for latex lineno package.
    #onecolumn: TRUE # Uncomment for one column format; default FALSE
    extra_dependencies:
      - booktabs # to use with knitr::kable() example below
      
## Example of pandoc's variable
#urlcolor: orange
#linkcolor: green
#citecolor: red
header-includes:
  #- \usepackage[nomarkers,tablesfirst]{endfloat} # For figures and tables at end
  - \theoremstyle{thmstyleone} # Theorem stuff from OUP template
  - \newtheorem{theorem}{Theorem} #  meant for continuous numbers. %%\newtheorem{theorem}{Theorem}[section] # meant for sectionwise numbers. optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
  - \newtheorem{proposition}[theorem]{Proposition} # %%\newtheorem{proposition}{Proposition}" # to get separate numbers for theorem and proposition etc.
  - \theoremstyle{thmstyletwo}
  - \newtheorem{example}{Example}
  - \newtheorem{remark}{Remark}
  - \theoremstyle{thmstylethree}
  - \newtheorem{definition}{Definition}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, # By default, hide code; set to TRUE to see code
  fig.pos = 'th', # Places figures at top or here
  out.width = '100%', dpi = 300, # Figure resolution and size
  fig.env="figure",
  options(digits =  2)
) # Latex figure environment

options(knitr.table.format = "latex") # For kable tables to write LaTeX table directly
```

# Kelly Criterion Concept

The (Continuous) Kelly Criterion provides a way to calculate the optimal fraction of wealth to invest in each available opportunity to maximize the exponential rate of growth of the investor's wealth.

-   To protect risk of ruin: equity go to zero.

**Kelly function**

1.  Input

\- $E$ : excess mean return

\- $\sigma^2$ : variance return

2.  Formula $$f^* = E/ \sigma^2$$
3.  Output

\- $f^*$ : Optimal fraction of investment

**Maximum compounded growth rate**

1.  Input

\- $S$ sharp ratio of portfolio

2.  Formula $$g = S^2 / 2$$
3.  Output

\- $g$ : long term growth rate (expected annual compound return)

## Assumption

Order in restriction:

1)  Future probability distribution of return is the same as the past. [All cases]
2)  Future probability distribution of strategy's return is the same as the past.
3)  Probability distribution of return of the strategy is Gaussian.
4)  Central theme: leverage should keep constant.

## Practical Usage

-   Use half-Kelly leverage or apply submaxomal compounded growth rate.
-   Use it as an upper bound of leverage.

## Function

```{r, echo = TRUE}
# Kelly Criterion function 
calc_optimal_f = function(return, sd){
  optimal_f = return / sd ^ 2
  return(optimal_f)
}
```

```{r, echo = TRUE}
# Compound growth rate
calc_growth_rate = function(return, sd){
  sharp_ratio = return / (sd ^ 2)
  growth_rate =  (sharp_ratio ^ 2) / 2  
  return(growth_rate)
}
```

## Example

```{r,echo=TRUE}
return = 0.1123
risk = 0.1691
paste("optimal f:" , round(calc_optimal_f(return,risk),2))

```

# Optimal allocation among strategies.

```         
```

here is the example of equation

$$
E=mc^2
$$

An inline equation: $y=ax+b$

An equation with a label for cross-referencing:

```{=tex}
\begin{equation}\label{eq:eq1}
\int^{r_2}_0 F(r,\varphi){\rm d}r\,{\rm d}\varphi = 1
\end{equation}
```
# Note

1.  Kelly $f$ is independent of time scale: annual or daily share the same value
2.  Sharp ratio is time scale dependent
3.  Should include sharp after cost.
4.  Risk free = 0

The code below creates a figure. The code is included in the output because `echo=TRUE`.

```{r fig1, fig.cap="This is the first figure.",echo=TRUE}
plot(1:10,main="Some data",xlab="Distance (cm)",
     ylab="Time (hours)")
```

You can reference this figure as follows: Fig. \ref{fig:fig1}.

## Figures spanning two-columns

Figures can span two columns be setting `fig.env="figure*"`.

```{r fig2, fig.cap="This is a wide figure.",fig.env="figure*"}
plot(1:5,pch=19,main="Some wide data",
     xlab="Distance (cm)",ylab="Time (hours)")
```

Reference to second figure: Fig. \ref{fig:fig2}

# A5 Intro

## Generate a table using `xtable`

```{r xtabletable, results="asis", echo=TRUE}
df = data.frame(ID=1:3,code=letters[1:3])

# Creates tables that follow OUP guidelines 
# using xtable
library(xtable) 
print(xtable(df,caption="This is a xtable table.",
             label="tab:tab1"),
      comment=FALSE,caption.placement="top")
```

You can reference this table as follows: Table \ref{tab:tab1}.

## Generate a table using `kable`

```{r kabletable, echo=TRUE}
df = data.frame(ID=1:3,code=letters[1:3])

# kable can alse be used for creating tables
knitr::kable(df,caption="This is a kable table.",
             booktabs=TRUE,label="tab2")
```

You can reference this table as follows: Table \ref{tab:tab2}.

## Table spanning two columns

Tables can span two columns be setting `table.envir = "table*"` in `knitr::kable`.

```{r widetable, echo=TRUE}
df = data.frame(ID=1:3,code1=letters[1:3],
                code2=letters[4:6],
                code3=letters[7:9],
                code4=letters[10:12],
                code5=letters[13:15])

# kable can alse be used for creating tables
knitr::kable(df,caption="This is a wide kable table.",
             #format="latex",
             table.envir="table*",
             booktabs=TRUE,label="tab3")
```

# Cross-referencing sections

You can cross-reference sections and subsections as follows: Section \ref{literature-citations} and Section \ref{a-subsection}.

***Note:*** the last section in the document will be used as the section title for the bibliography.

For more portable and flexible referencing of sections, equations, figures and tables, use [`bookdown::pdf_document2`](https://github.com/rstudio/bookdown) with YAML header option `base_format: rticles::oup_article`.

# A6 Intro

::: {.appendices latex="true"}
# Section title of first appendix

blabla

## Subsection title of first appendix

and so on....
:::

# References
